---
title: "Proposal Outline (draft 1)"
author: "Max Brubaker"
date: "12/8/2021"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction:

__*It is the aim of this project to discern how the carbon functionality of soil fungal communities compares among different forest successional stages*__. The lack of clarity in the literature regarding old growth forests and their ecosystem function (__*cite those papers arguing*__) demands further understanding in the contribution of forest life history strategy. From simple definitions It is our belief that belowground forest communities are vastly misrepresented in the literature today. Additionally, what little research has been conducted on these belowground communities has lacked an approach that is vital to understanding functionality. This project will focus on fungal communities in the soil systems for (NUMBER) reasons. First, fungi have been shown to be the most dominant, etc. etc. in forest systems. Furthermore, as systems age and shift into late sucessional/old growth stages, fungi dominate the microbial community. Our approach differs from past research in that we are not specifically focused on who is there (although this will be a by-product of our analysis). Instead, we focus on *what* these fungal communities are doing through fungal transcriptome analysis. Old growth forests are extremely dynamic, productive, and resilient systems. If we can shed light on how the functionality of the soils are changing as forests age, it may very well dictate how we continue to treat these systems moving forward. The authors of this paper want to make it clear that this is NOT an attempt to develop a new way to classify old growth forests. However, depending on the results of this paper it may very well open the door to new considerations. It is our belief that this research will provide the information to make clear decisions for future management practices through examination of how exactly these forest systems differ in terms of fungal soil carbon functionality. Additionaly, pending the results of this paper, it is suggested that future research analyze other microbial communities through a similar approach with a goal of understanding how these old growth forests as a whole function differently from younger forest systems


To achieve this we will analyze consequence stages established in (TIME) *CITE* in the east and west old growth forests of Vancouver island (see materials and methods for further details).  


```{r}
#(notes): what is the real contribution. Open with the question we are asking. 
#-	More “modern” approach” : start with research gap, what’s the hole and why does it matter/why do we need to know it. 
  #- What is wrong and why do we care about it
	#- Based on the “story” we want to tell
#What do we know about soil fungal communities over time?
  #- Summarize what we know and highlighting what we do not know. 

#BIGGEST THING IS TO TELL AN INTERESTING STORY WHITHOUGHT BLABBERING:
  #-	Where is the thread…. (Tanjiro ~ find the thread)
  #-	Not a single word or syllable that is not needed. 
  #-	Parsimonious with language*** this leads to power
    #-Cell, Nature, Science are so well written because EVERYTHING that is not needed is taken out. 

```














__Intro to Old Growth Forests:__

- Significance of OGF (general and in Canada) 
- % of forest lost
- OGF Ecosystem services
- Other impacts/qualities of OGF... end with something saying how the most abundant microbes in OGF are fungi, leads into...

__Introduction to Fungi__  *(in OGF)* :

- Fungal soil contribution/function

__Introduction to Carbon__ *(in OGF)* :

- See what I can find about carbon in OGF, if anything I can discuss the contrast in the literature
 

# Successional Fungal Community Structure: (soil and fungi?)
- General understanding of fungal community structure as forest age increases
- Longitudinal variation (Kristen mentioned someone...)
- Elevation variation 
- Soil characteristic 
- Environmental conditional changes:
  - Warming
  - Changes in CO2
  - Soil moisture
  - Tillage/physical disturbance 
  - Other chemical disturbance




# Fungal Communities and Carbon Dynamics: (tied into above) :
- Fungal Carbon Functionality
- Carbon sequestration
- Carbon cycling
- Carbon degradation
- Carbon …


# Research Hypothesis:



# Materials and Methods (experimental design):



# Project Timeline:



# Literature Cited:


*Maybe end the intro with the gap I am aiming to fill?* : *ex:* : An over arching issue when we consider analyzing these systems is the lack of clarity in the literature. From simple old growth forest definitions to understanding the below ground activities, is is apparent that there is much to learn about these systems. It is our aim to provide a new look at observing old growth forests by analyzing the soil fungal communities. 


```{r, echo=FALSE}
#I had this as another subheading but it seems repetative


#Fungi in Old Growth Forests: (tied into above) ???
#Seems to be a general understanding that as forest ages increase fungi become more dominant
```







Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
