---
title: "Draft 1"
author: "Max Brubaker"
date: "12/10/2021"
output:
  word_document: default
  html_document: default
bibliography: Proposal Draft Bib.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
__BIG QUESTIONS--:

```{r}
#What if, as a part of my thesis or even just as a lab... why don't we aim to standardize soil measurement strategies, definitions,, protocols.. we need to be doing these things on equal levels in order to be able to properly compare/contrast/understand. 
  #- could seek through SES and just discuss with individuals.

  #- how can we ensure that we are measuring as universal as possible? *steming from the SES discussion. We need to be making measurements and definitions __common use__*.

```

# Introduction Information
*questions*: Why do we care about knowing soil fungal carbon functionality?

+ fungal communities are primary decomposers
+ fungal communities are some of the only decomposers that can break down lignin and cellulose. 
+ fungal communities are dominant in old growth forest systems
    - need support in old growth systems functionality.. are they are more productive or biodense? 
+ regardless of support or rejection of old growth forest logging we are drastically reduce a (more or less) finite resource. This resource contains *information*.


overall goal / message to display is that we do not know how these forest soil microbial communities differ in terms of functionality. (INSERT CARBON) This is a huge issue as we are making major decisions (such as logging old growth forests) without fully understanding the below-ground processes. We are running under this assumption that old growth forest soils are the same (or at least operate the same) as younger/managed soil systems. 

I think the overall message or story I want to tell is that these systems are dynamic and that AGE MAY INFLUENCE FUNCTIONALITY. I retain an unbiased nature as to whether or not these older systems are more "functional" than younger systems but I can without a doubt say that we need to understand them more fully before we continue to decimate and eradicate them.

#### What points will support my thoughts on this?
  + We know that forest communities change over time
  
  + We *know* that microbial community influences functionality (NEED MORE RESEARCH ON THIS)
      - microbial communities influence soil chemistry, plant community, above-ground and below-ground biodiversity
      - these are all dynamic attributes... each are linked and as one changes resulting changes will follow... 
      
  + I need to have a better understanding of HOW current forest soils are being assessed... (NEED MORE RESEARCH ON THIS)
  
  + Need more information on how microbial communities change over time. 
  
  + Need specific examples showing that we are only looking at WHO is there rather than WHAT the are doing*. 
      - eukaryotic transcriptomics.
      
  + Need some information showing functionality of different forest succession stages.
  
  
  
```{r, echo=FALSE}
#Notes from Mirandas Video: 

# opportunity to frame your story (1-3 pages)

#what is your question? - by the end of the first paragraph readers should know what your question is and why it is important.

#Very important to stick to the point and focus on the topic.

#Why are we asking the question and what is the gap we are trying to fill.

#Once you are finished with the first paragraph. The remaining paragraphs should act as stand alone essays.

#By the end of the introduction the readers should have JUST ENOUGH information of why this is an important question to answer and the general context. Non scientist should be able to read this and understand.
  
```

\newpage

# Introduction Paragraph

Current unknowns and controversies in the literature among old growth forests demand a more collective understanding of the fate and function of these systems. A recent example of such controversy is shown (@Luyssaert_2008, @Gundersen_2021, and @Luyssaert_2021) in the debate over the functionality of old growth systems in terms of their carbon sequestration capabilities. We believe that the misrepresentation of the below ground community is a significant contributor to not only contrasting findings such as these, but also to the lack clarity in soil science and ecosystem functionality as a whole. This study aims to determine how soil fungal communities differ among forest sucessional stages (SS's) in community structure and carbon functionality. Emerging research suggests that increase in forest SS may be associated with a number of below-ground processes. For example, it is evident that microbial community composition responds to forest SS development. As forest age increases we see a shift from a r-strategic dominated community (variable environment dominated by bacteria) to a k-strategic dominated community ("stable" environment dominated by fungi)  [@Sun_2021, @Yan_2020, @McGee_2019, @Zhou_2017, and @Zhou_2017b]. Additionaly, this increase in SS has been accompanied by an increase in microbial biomass (@Zhong_2018 and @Yan_2020). Contrarily, we see reductions in both microbial biomass and diversity when forests are reverted to *stand initiation* stages (@Rodriguez_Ramos_2020, @Zhong_2018), with variation depending on disturbance type. It is clear in the literature that both physical and chemical disturbance can lead to substantial changes in the microbial community. Fungi have been chosen as our model organism to analyze soil microbial community and functionality. A number of studies have analyzed fungal community composition in search of "who is there", but far less have looked into soil functionality through fungal community analysis in terms of "what are they doing". There is evidence suggesting a positive correlation between soil microbial diversity and soil ecosystem functionality [@Delgado_Baquerizo_2016]. Understanding the link between microbial community composition and forest functionality is crucial for future forest management and preservation. It will be a part of this project to test the ability of different genomic community analysis methods to provide information regarding a soil microbial community. We are aware that a experiment such as this could easily take up the entirety of a Ph.D. and that environmental sample are notoriously difficult to accurately measure in terms of genomics. We will analyze inoculated soils with known microbial communities and test the ability of certain methods (whole genome sequencing, metagenomics, and metatranscriptomics) to provide accurate representations of said community. The results from this experiment will dictate our future community analysis methods. We hope that this project will provide insight towards whether or not old growth forests are functionally different from managed systems as an understanding such as this may shape future forest ecosystem analysis and the resulting management practices. 

__*if this is the goal that means i need to add a little emphasis on the deterioration of the old growth forests and problems with losing these systems (objectively)*__
    + could add this to the next paragraph regarding fungi and old growth forest deterioration.

```{r, echo=FALSE}

#COULD ADD IF THIS WAS THE CASE BUT ITS WAY OVERTOP FOR NOW... 

# A requirement prior to completion of this study was to be first in attempts to begin developing global soil sampling methods. Such attempts were made by connecting with x soil biologists in x different countries and establishing unanimously agreed upon soil sampling methods. (stoned idea, maybe separate publication? Would be really cool to link with my project. )

# __*intro sentence*__ : The lack of clarity surrounding so many aspects of old growth forests and soil science in general creates great difficulty in inference and decision making. (not a fan of this)

#  + could go into controversy of OGF as carbon sources/sinks and how this is something we cant even make a decision on without understanding the functionality of the below-ground ecosystem.
#  + could also talk about the issue of not replicating sampling methods among soil science, this is a huge issue because it means we cannot compare our data and our findings. If everyone is doing something different in attempts to measure or determine the same thing, no wonder one group of people are finding one thing and another group are finding the opposite.
```
... 

#Second Paragraph: (needs to build off a main point from the intro and needs to have a strong lead sentence) 

Is it imoprtant to discuss how fungi are involved in ecosystem function? Even just a brief paragraph to support why we are looking at fungi as opposed to another group of microbes? could add in carbon maybe


#Third Paragraph: 


__*intro sentence*__ :Understanding how shifts in microbial community impact ecosystem functionality with forest succession, and how the resulting soil characteristics respond, can greatly improve our ability to infer how ecosystems are influenced by environmental change. The findings of @Delgado_Baquerizo_2016 suggest ecosystem functionality is dependent on specific microbial diversity and that a shift in said diversity is likely to change the functionality and resulting ecosystem previsions/services. It is apparent that as forest systems transition into later successional stages, we see a major change in microbial ecosystem diversity (@Yan_2020 and @Zhou_2017). These, among other studies (@Sun_2021 and @Zhou_2017b), show that as forests age we see a shift from an r-dominated to a K-dominated microbial community. This is important as it not only shows that as forests age we shift into a fungal dominated soil ecosystem, but it also suggests that fungi are associated with forest ecosystem "stability" (see r/k-strategists for details). Furthermore, we see (@Jiang_2021) that the relative abundance of certain fungal communities significantly increase with succession. Conversely, it has been shown that bacterial groups decline or remain relatively unchanged along successional gradients (@Zhou_2017b, @Yan_2020). This suggests that fungi may become more involved in nutrient cycling as forest ages increase, or that bacteria are able to maintain functionality in different soil and environmental conditions. Understanding which organisms are present in soil systems is extremely important and there is a substantial amount of research present in the literature eluding to how microbial community composition changes among kingdoms (bacteria, fungi, etc) as forest age. Digging deeper, a majority of fungal community analysis revolves around genomic sequencing in search of the presence or absence within specific hierarchical classifications (i.e. phylum, class, genus, etc). However, this leaves us with massive oversight as to how these changes in community impact the corresponding ecosystem functionality.  

could transition into genomics paragraph....


#Fourth Paragraph: (need more literature review)

__*intro sentence*__ : Understanding how functionality and microbial community change over time is crucial however, natural undisturbed succession is becoming increasingly rare by the day. Ecosystem disturbance is happening more frequently via both natural (extreame weather) and anthropogenic (logging/management) means....info on how disturbance influences microbial community........ It is also important to understand that the type of disturbance may impact how the microbial community changes. Needs work, maybe add stuff how we need to maintain old growth systems and stuff...                                                               




#Fith Paragraph:

__*intro sentence*__ ..... maybe talk about parameters that have been shown to change as successional stages increase???




#Last Paragraph before conclusion:

__*intro sentence*__ The last paragraph could touch on the lack of clarity in old growth analysis and how current decisions, controversies, etc do not even consider that forest functionality may change with age/lack of disturbance. 







@Jiang_2021: Bacterial and *Fungal* community composition and functional changes with forest succession:
 
  #  - The results showed that forest succession significantly changed the community composition of bacteria and fungi, among which the fungal community was more sensitive to the changes with successional stage.

  #  - *** In this study, the soil total carbon and total nitrogen were the dominating factors affecting the soil microbial community and the structure of           fungal functional groups..
      




@Yan_2020: Fungi and beacteria functional genes ~ chronosequence
      - Soil microbial biomass (C, N and P) increased significantly in topsoil (0-20 cm) with vegitation succession.
      - Fungal abundances annd the Fungal:Bacterial was detected along a successional gradient (???)
  
      - C and N cycle-related (potential) functional genes increased significantly and then stabbilized (*)
      - recalcitrant C degredation, N reduction, and denitrification-related genes increased and labile versions decreased
      - __fungal communitie were most correlated with ammonium N contents and root biomass__






```{r, echo=FALSE}
#I think the below text should be the next paragraph but maybe not in the intro paragraph?
```


It is our belief that a significant portion of controversy/uncertainty in old growth forests (see [@Luyssaert_2008, @Gundersen_2021, @Luyssaert_2021] for example) can be contributed to the lack of understanding in below-ground processes (CITATION?).

Above-ground forest processes have been studied for over a century (CITATION) and with this knowledge many regulations have been set in place. It has been noted (CITATION ~ somewhere in ogf book?) that many of these regulations have been set in place based almost soley on above-ground processes. Additionally, if in fact below-ground processes are considered, we are using "blanket understandings" of these systems as if they are all the same. 

```{r, echo=FALSE}
# i hate most of the text above this
```

While controversy is ever present and results are variable potential trends may be emerging with the increased study of old forest chronosequences (CITATIONS?) stretching into the __*standardized old growth forest ranges*__. A number of soil characteristics are appearing correlated with forest successional stage. 

```{r, echo=FALSE}
#Clean ^ up and make it a bit more impactful
```




```{r, echo=FALSE}
#Next would be great to throw in a (supported) statement showing how forest age influences functionality...

# @Martin_2021: (Coniferous closed canopy) Wild fire vs Logging disturbance.
   # - concerns with targeting of high economic forests in logging practices. This suggests a targeted reduction in specific habitats

  # - Wood volume, basal area, tree density, stand height and broad leaved proportion were, respectively, 45.6, 33, 20, 19.5, and 41.5% higher in logged stands compared to the burned ones. Logged stands were thus denser and more productive than burned stands, resulting in a higher wood volume.

  #  - this idea of "remnant" forests. It seems refers to undisturbed forest systems within a managed area..? (need to fact check this)
   #   - if so, my understanding is that even though these remnant systems are "undisturbed" they are often found to be lower in productivity along with other reduced forest characteristics such as woody biomass or stand density.
    

# @W.Wang_2011: linking above-ground carbon stocks relative to forest structural diversity. 
   # - kind of a weak paper/journal, lots of citations tho. 

   # - indicate that as stand structural diversity increases so do above-ground carbon stocks
      #    - This occurs because complex forest structures allow for greater light infiltration and promote a more efficient resource use by trees, leading             to an increase in biomass and C production. 


# @G.Wang_2021: Secondary succession and fungal/bacterial community composition (karst area)
    # - Conversely to what I have been seeing, there was an initial increase in fungal diversity during succession, followed by a decrease.
    # - Total P was the most important environmental factor and positively effected fungal diversity. (pH was another important factor)
    # - Soil Fe and Cu negatively impacted fungal diversity. 
    # - Ascomycota decrease and basidomycota increase as time without disturbance increases




# ****  @Qu_2020: bacterial community and functional changes with forest succession
    #- not a ton of useful info other than it shows as forest succession changes, as does the microbial communities and soil functionality

# ****  @Jiang_2021: Bacterial and *Fungal* community composition and functional changes with forest succession:
   # - used 16S and ITS rRNA gene sequencing to detect bacterial and fungal communities and used FAPROTAX and FUNGuild database to predict bacterial and         fungal functional groups. 

  #  - The results showed that forest succession significantly changed the community composition of bacteria and fungi, among which the fungal community was more sensitive to the changes with successional stage.

  #  - *** The relative abundance of ectomycorrhizal fungi significantly increased with succession, while the relative abundance of bacterial functional groups involved in the nitrogen cycle did not change significantly, indicating that fungi might play a major regulatory role in the nutrient cycling process during the successional process.

  #  - *** In this study, the soil total carbon and total nitrogen were the dominating factors affecting the soil microbial community and the structure of           fungal functional groups..
      
      
# @Whitefeld_2014: forest system succession and the resulting species composition and functionality (plant focused)
  #    - a bit of a weaker reference but held many citations. 
  #    - Data found that: as succession proceeds, communities occupy a greater range of functional trait space even after controlling for stem and species density. **** High functional diversity is important for ecological resiliency in the face of global change.
      
      
# **** @ Liu_2020: Bacterial and fungal** analysis of ~160 secondary succession (chronosequence)
   #   - During succession, soil bulk density, soluble carbon, total nitrogen and plant richness had large effects on the microbial community.
   #   - Most prominent changes in community occured in early succesion with "relative stabilization" during late succession
   #   - Decrease in ascomycota over time and an increase in basidiomycota overtime. Actually basidios were the only ones to show an increase over time
   #   - bacterial and fungal absolute abundances become stable after S3 (110 years), which is consistent with the results of Darcy et al.(2018).
      
      
      
# **** @Yan_2020: Fungi and beacteria functional genes ~ chronosequence
  #    - Soil microbial biomass (C, N and P) increased significantly in topsoil (0-20 cm) with vegitation succession.
  #    - Fungal abundances annd the Fungal:Bacterial was detected along a successional gradient (???)
  #    - microbial communities shift from r- to K- strategists??? both that the phylum and genus level.
  #    - C and N cycle-related (potential) functional genes increased significantly and then stabbilized (*)
  #    - recalcitrant C degredation, N reduction, and denitrification-related genes increased and labile versions decreased
  #    - __fungal communitie were most correlated with ammonium N contents and root biomass__


# @Delgado_Baquerizo_2016: Forest multifunctionality is associated with microbial biodiversity.
  #    - Reports that soil microbial diversity positively relates to multifunctionality in terrestrial ecosystems. 
  #    _ Our findings provide empirical evidence that any loss in microbial diversity will likely reduce multifunctionality, negatively impacting the provision of services such as climate regulation,soil fertility, and food and fiber production by terrestrial ecosystems.



# @Zhou_2017: trends in mcrobial community along secondary succession:
  #   - The results showed that the fungi to bacteria ratio (fungi:bacteria) increased, while the microbial respiration per unit biomass carbon (R/Cmic)           decreased as the succession proceeds. 
  #   - Secondary succession had the rising trends in microbial biomass carbon to soil carbon ratio (Cmic/Csoil) and microbial biomass nitrogen to soil nitrogen   ratio (Nmic/Nsoil).
  #   - Early successional stages tended to be dominated by r-strategists (bacteria) that had higher R/Cmic and lower Cmic/Csoil and Nmic/Nsoil, whereas late     successional stages tended to be dominated by K-strategists (fungi) that behaved oppositely. ***** 
  #   - The soil C to N ratio (C:Nsoil) increased significantly with the successional stage, with a fast increasing C:Nsoil ratio being accompanied by a fast      increase of fungi:bacteria, a slow decrease of R/Cmic, and a slow increase of Cmic/Csoil. This


# @Zhou_2017b: Effects of forest degradation on microbial communities and soil carbon cycling: meta analysis.
  #   - forest degradation decreased k-strategists (fungi) and increased r-strategists (bacteria)
  #   - in the process soil properties changes, and there was a stimulation in microbial activity and C-decomposition


# @Bowd_2021: Distrubance alters microbial community:
  #   - Indicates that disturbance negatively impacted microbial diversity. (different disturbance different impact)
  #   - Soil pH, manganese, magnesium, phosphorus, iron and nitrate were associated with the composition of all microbial communities.
  #   - Some specific info on types of fungi found in different areas of soil. 


# @McGee_2019: Bact & fungal community composition and CUE in different forest successional stages (primary, seondary(33yrs), and young secondary (22yrs))
  #   - We found that soil Cmic (soil microbial biomass carbon) levels increased along the management gradient from young, to old secondary, to       primary forest. 
  #   - In addition, the changes in soil Cmic and soil fungal community structure were significantly related to levels of soil NO3
  #   - Analyses showed that even after 33 years of natural forest regrowth, the clearing of tropical forests can have persistent effects on soil     microbial communities and that it may take a longer time than we realized for secondary forests to develop carbon-utilization efficiencies       similar to that of a primary forest. 
  #    - Results also indicated that forms of inorganic N may be an important factor in structuring soil Cmic and the soil microbial communities,     leading to improved CUE in regenerating secondary forests. This



# @Rodriguez_Ramos_2020: Fungal community change with disturbance.
  #    - significant change in fungal biomass, minimum of 43% decrease depending on the *type* of disturbance
  #    - major decreases in SOM with disturbance
  #    - abiotic disturbances changed community composition (see paper for details).

# @Rodriguez_Ramos_2020b: Influence of anthropogenic disturbance on fungi and a pine seedling.
  #   - disturbance alters soil fungal community and functionality which in turn impacted the seedling. This could be useful if I decide to discuss          how fungi community impacts ecosystem functionality.  


# @Sun_2021: fungi/bacteria community response to CO2.(meta-analysis)
  #   - nothing particularly special about this paper at first glance
  #   - As CO2 levels increase, we see a shift from K (fungi) to r (bacteria)
  #   - this observation was consistent among different biomes (forest, grassland, etc.)

# @Callado_2021: Impacts of forest thinning on fungal community (above-ground)
  #   - Forest thinning impacts fungal community diversity


# @Zha_2022: microbial functional genes and soil quality
  #   - A significant positive correlation was found between the abundance of microbial C decomposition genes and priming effects (p < 0.05).               Further analysis revealed that the microbial functional genes for breaking down stable C (lignin, lipids, and chitin) predominately drove           the positive priming effects. 
               #- to me this suggest a correlation between fungi and priming effects 


#@J.Wang_2019: temporal turnover trends fungi and bacteria
  #   - Consistent with previous findings that as time increases fungi become more dominant
  #   - also supports previous findings that basidos dominate late while ascos dominate early
  #   - also supports a finding that I noticed stating that fungi are more sensitive to environmental change
  #   - fungal succession was affected to a greater extent by NO3, -N, available P, and C:N ratio.

#@Correia_2021: Land-use history alters the diversity and community composition of ECM
  #   - "Land-use history modulated the mycorrhizal symbiosis in regenerating beech forests through changes in soil organic matter and nitrogen,          which were the main drivers of the differences in fungal community composition and functional types associated with beech trees in recent           forests."



#@Chen_2019: Contrasting patterns and drivers of soil fungal communities in subtropical deciduous and evergreen broadleaved forests.
  #   - "plant diversity and litter biomass were the main above-ground drivers of fungal diversity and composition in the deciduous forest, while            host effects were prominent in the evergreen forest."
  #   - "soil pH, water content, and nutrients (especially available P), were identified as the primary drivers of soil fungal communities in the            broadleaved forests"
  #   - Evergreen forests showed less environmental variability in fungal communities.


#Chen_2020: *strong* association between fungal community composition and soil quality ~ Chronosequence (Chinese Fir Plantation)
  #   - Very interesting abstract.. need a full read through. But it explains the idea that topsoil quality is related to the dominant type of fungi
  #   - Younger forests with lower amounts of litterfall are associated with decrease in soil nutrient availability and are therefor dominated by         mycorrhizal fungi. As forests age and litter increases (fact check this), we see shifts towards saprotrophs to increase OM degredation. In          turn this leads to an increase in soil nutrient availability.
  #   - Fungal diversity (OTU richness) increased with stand age in the 0–5 cm layer, and was overall higher than in the 5–15 cm layer.
  #   - Fungal diversity was negatively correlated with avaliable P, and positively correlated with NH4+ and acid phosphitases (??)
  #   - CONTRASTING finding - ascomycota increased with stand age and basidomycota decreased.. 
```








































































\newpage


# Expiremental Design:

__**We are going to be analyzing soil fungal communities (meta - genomics,transcriptomics) of forest successional stages*__:

What parameters would also be interesting to know wth forest age (successional stage)?
    -__Q__: how are we defining forest "age" or successional stage. What range of area does this account for? What area do we sample over? How many areas will we measure to consider that forest covered? this leads back into how are we classifying forest stage (stand age only? how was stand age measured (check ogf book on that one))
    -__Q__: are we accounting for type of disturbance? Because im pretty sure I have seen that type of disturbance may result in different forest response (Natural vs. athropogenic)



Parameters:
  - climate: temp, humidity, etc.
  - topsoil (%, depth, ratio, whatever)
  - lat,long, and elevation (analysis within systems?)
  - soil moisture
  - Field pH?
  - 
  - % fungal biomass
  - % rna expression
  



Samples: how are we sampling? Is it possible to gps every sample? In theory gps samples could allow us to account for auto correlation between sample and  are we breaking sampling methods down likey Tony or different? We need to make sure that we we are doing can remain constant across forests/sampling locations.
  - I feel like I tossed a grid idea around... what if you took 




